%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
	%---------------------------------------------------------
	\cventry%
	{Research Intern} % Job title
	{CERN} % Organization
	{Largest particle physics laboratory in the world}
	{Geneva, Switzerland} % Location
	{Jun. 2024 - Present} % Date(s)
	{https://andresnav.com/posts/i_got_accepted_at_cern_and_this_is_how/} % URL
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Optimized and developed a Python library for research in gas particle detectors.}
			\item {Collaborated with highly specialized professionals, enhancing programming skills and advanced software development practices.}
			\item {Implemented automatic DevOps pipelines for automatic testing.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry%
	{Cloud \& ML Research Technician} % Job title
	{UC3M} % Organization
	{Among the top universities in Spain}
	{Madrid, Spain} % Location
	{Jul. 2023 - Present} % Date(s)
	{https://www.linkedin.com/company/saeta-uc3m/} % URL
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Responsible for designing and architecting a distributed infrastructure in the cloud for 100+ users using Terraform and Docker.}
			\item {Implemented CI/CD pipelines to accelerate the deployment by 5x across 10+ devices around Spain.}
			\item {In charge of go-to-market strategies. Proposed scalable and cost-efficient solutions to stakeholders.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry%
	{Cloud \& ML Team Lead Engineer} % Job title
	{SAETA} % Organization
	{UAV University Association}
	{Madrid, Spain} % Location
	{Sep. 2023 - Present} % Date(s)
	{} % URL
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Led the development of efficient ML pipelines with AWS to train models with 100+ GiB of data.}
			\item {Entrusted with the security of AWS Organization account for 50+ users with best practices and zero breaches}
			\item {Accountable for optimizing cloud costs with data analysis by reducing 5x.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry%
	{ML Team Lead Engineer} % Job title
	{} % Organization
	{}
	{} % Location
	{Feb. 2022 - Sep. 2023} % Date(s)
	{} % URL
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Coordinated a team of 3+ engineers from the beginning, focusing on teamwork and cooperation.}
			\item {Carried out the development and tuning of neural network models with an accuracy of 97\%.}
			\item {Developed data augmentation and validation systems to extend the dataset 50x.}
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Participant at Summer of Nix 2023} % Job title
	{NixOS Foundation} % Organization
	{Declarative and Functional Linux Distribution}
	{Remote, Europe} % Location
	{Jul. 2023 - Oct. 2023} % Date(s)
	{https://summer.nixos.org/} % URL
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Collaborated with 4 engineers around Europe by packing software with Nix and Docker for reproducible deployments.}
			\item {Contributed to an open-source mono-repo with 30+ engineers, redesigning it for proper scalability.}
		\end{cvitems}
	}

	%---------------------------------------------------------
\end{cventries}
